Big Ideas in Sports Analytics and Statistical Tools for their Investigation

### 2022-07-16 sports_analytics.Rmd
1 additional sentence on epv soccer

erm |>
  pivot_wider(names_from = Out, values_from = Runs) |>
  mutate(Base = int2bin(Base)) |>
  kable(booktabs = TRUE, 
        caption = "George Lindsey's expected run matrix. Note how (when reading across the rows) the expected runs decrease as outs increase for the same configuration of baserunners, while (when reading down the columns) expected runs generally increase as baserunners advance. \\label{tab:erm}") |> 
  add_header_above(c("", "Out" = 3))
```

@@

The notion of EPV has also been extended to soccer.
@fernandez2021framework implement deep learning methods to examine the instantaneous expected value of soccer possessions. 
This approach considers passes, ball drives, and shots in soccer as the main set of actions used to compute expected possession value.

>>>>

erm |>
  pivot_wider(names_from = Out, values_from = Runs) |>
  mutate(Base = int2bin(Base)) |>
  kable(booktabs = TRUE, 
        linesep = "",
        caption = "George Lindsey's expected run matrix. Note how (when reading across the rows) the expected runs decrease as outs increase for the same configuration of baserunners, while (when reading down the columns) expected runs generally increase as baserunners advance. \\label{tab:erm}") |> 
  add_header_above(c("", "Out" = 3))
```

@@

The notion of EPV has also been extended to association football (soccer.)
@fernandez2021framework implement deep learning methods to examine the instantaneous expected value of soccer possessions. 
This approach considers passes, ball drives, and shots in soccer as the main set of actions used to compute expected possession value. 
Many applications can be derived from this framework, including predicting which footballer is most likely to receive the next pass from the current on-ball player.
